paper1_figures

### 2024-01-05 scoping_review_short.Rmd
third version, 05.01

@@

The way cooperation was operationalized was deeply connected to the study's setting. In fact, experiments based in laboratory often observed participants' distribution of resources between themselves and a group account to quantify their cooperation. The most used method (*N*=33) was to endow participants with an amount of a resource (often real or fictive money), and see which part they invested in a public account, from which the whole group could benefit. Otherwise, researchers observed which amount of the resource participants took for themselves from a collective pool (*N*=7), or how much they gave to an interaction partner (*N*=4).[^5] Another method often used in laboratory studies was to give participants the choice between cooperation and defection (*N*=18). Interestingly, in laboratory settings, words like "cooperation" or "defection" were rarely used during the instructions, to avoid responses dictated by social desirability.

@@

<!--# in the text: tables with the name of factor, the papers, the main effect and a list of moderatorsin Annexe: same table, but with more details for each moderator effect is it useful to put in both tables the analyzed papers for each factor?-->

@@

|                                                               | @Dorrough2019; @Peshkovskaya2017; @Balliet2011; @Spadaro2023; @Sell2009; @Gomez-Ruiz2020; @Colman2018; @Peshkovskaya2019; @Barrero-Amortegui2021; @Simpson2003; @Irwin2015               |                                                                                                 |                                                                  |
|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Group composition                                            |

@@

|                                                               | @Aksoy2019; @Kingsley2016; @VanLange2013; @Chen2022; @Camera2020; @VanKlingeren2021                                                                                                      |                                                                                                 |                                                                  |
|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Group composition                                            |

@@

|                                                               | @Arora2016; @Noonan2016; @Gomez-Ruiz2020; @VanVugt2009; @Zhang2019; @Chen2007; @Wit1992; @Dorrough2015; @Aksoy2019; @Puurtinen2009; @Nockur2020; @Kramer1984; @Jackson2011; @Jackson2012 |                                                                                                 |                                                                  |
|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Intergroup competition                                       |

@@

|                                                               | @Balliet2009; @Emonds2011; @VanLange1998; @DeKwaadsteniet2008; @Lu2019                                                                                                                   |                                                                                                 |                                                                  |
|                                                               |                                                                                                                                                                                          | Pro-environmental values are positively correlated to cooperation                               | -   Uncertainty about the number of members                      |
|                                                               | *N*=9 (other factors)\                                                                                                                                                                   |                                                                                                 |                                                                  |
|                                                               | @Sussman2016; @Fosgaard2019; @Kieslich2014; @Hilbig2018; @Kocher2017; @Schlosser2018; @Liu2009a; @Probst1999; @Chen2007                                                                  | Left-wingers are more cooperative than right-wingers                                            | -   Deliberation                                                 |

@@

|                                                               |                                                                                                                                                                                          | Individuals scoring high in humility and honesty cooperate more than those scoring low          | -   Inter- vs independent self                                   |

@@

|                                                               |                                                                                                                                                                                          | Individuals with high self-control, or with a high level of justice sensitivity, cooperate more | -   Perceived social norms                                       |

@@

|                                                               | @Balliet2013; @Lubke2021; @VanLange2013; @Kocher2015; @Smith2013; @Chaudhuri2002; @Oyediran2018; @Sturm2019; @Franzen2019; @Rompf2017                                                    |                                                                                                 |                                                                  |
|                                                               |                                                                                                                                                                                          |                                                                                                 | -   Uncertainty about others' intentions                         |

@@

## Organizational factors

On the organizational level, we identified four factors from the reviewed papers: incentives, communication, social norms and anonymity. As for the individual factors, in the following sections we detail the main effects of each factor, and we provide an overview of possible moderators. A remsume of the main effects can be found in Table 3, while more details about the moderators in Appendix A.

+-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+

@@

+=======================+=================================================================================+================================================================================+===============================================================+

@@

|                       | @Balliet2011a; @VanDijk2015; @Pfattheicher2018; @Nockur2021;                    |                                                                                |                                                               |
|                       | @Egas2008; @Milinski2012; @Kingsley2016; @Chen2022; @Xiao2016; @Rockenbach2019; |                                                                                | -   Type of interaction                                       |
|                       | @VanDijk2015; @VanVugt2009; @Schlosser2018; @Irwin2014; @Mulder2006;            |                                                                                |                                                               |
|                       | @Jacquet2011; @Nelissen2013; @Maier-Rigaud2010                                  |                                                                                | -   Other participants' characteristics and group homogeneity |

@@

+-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+

@@

|                       | @Balliet2010; @Bicchieri2002; @Janssen2014;                                     |                                                                                |                                                               |
|                       | @Koessler2021; @Adams2022; @Hopthrow2005; @Kumakawa2013; @Torsvik2011;          |                                                                                | -   Type of communication                                     |
|                       | @Feinberg2014; @Feinberg2012; @Giardini2021                                     |                                                                                |                                                               |

@@

|                       | @VonBorgstede2018; @Thogersen2008; @Rege2004;                                   |                                                                                |                                                               |
|                       | @Arora2012; @VanLange2013; @Bardsley2005a; @Weber2008; @Bicchieri2002           |                                                                                |                                                               |
+-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+

@@

|                       | @Wang2017; @Rege2004; @VanVugt2010a; @Butz2021;                                 |                                                                                |                                                               |
|                       | @Romano2016; @VonBorgstede2018; @Jiang2021; @Mosler1993;                        |                                                                                |                                                               |
|                       | @Przepiorka2020; @Koessler2021a                                                 |                                                                                |                                                               |
+-----------------------+---------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+

@@

The aim of the present paper was to synthesize the existing literature about cooperation in social dilemmas, in order to identify factors that could impact cooperative behaviours in commons. Through a scoping review approach, we identified nine factors, both at the individual and group level. Our results seem to be in line with others findings about cooperation in commons. For instance, factors such as gender, social status, SVO, incentives, and communication were also found by @Kopelman2002 in their review about lab-based commons, and their effects were the same as the ones reported in the current paper.

<!--# Put principles in the same order as presented in the introduction -->

Moreover, some of the factors can be related to Ostrom's principles to successfully manage a common resource [@Ostrom1990]. For instance, the clearly defined boundaries can strengthen commoners' social identification, since only when an in- and an out-group exist social identity is salient and therefore an identification is possible [@Tajfel1974]. Even if Ostrom developed this principle on a more organizational level, its secondary effect of creating a social identity can also contribute to improve cooperation. Secondly, communication is essential for the principle about the creation and modification of norms [@Bicchieri2002], and for the one about the arenas to solve conflicts. Finally, the principles concerning the monitoring and the graduated sanction systems underline the importance of incentives. The monitoring system refers to social incentives, and is linked to anonymity, since if people know that their behaviour can be observed, they are more willing to conform to social norms because they worry about others' approval [@Nelissen2013; @Rege2004]. On the other hand, a sanction system can also have a positive impact on cooperation [@Balliet2011a], especially if it is graduate, so if sanctions are not too high at the first violation [@Rockenbach2019].[^7]

[^7]: Principles 2, 7 and 8 refer to elements that are not pertinent to the current review, and therefore do not match any of the factors identified.

Ostrom's principles are especially related to factors at the organizational level. This is understandable when considering her economic approach to the study of the commons. However, taking into account the social dynamics and the characteristics of the commoners is also essential to have a better understanding of how these communities work [@Euler2018; @Nightingale2011]. For this reason, this paper went a step further and identified five individual characteristics affecting the efficiency of commons. Although less studied in commons literature, these individual factors are consistent with existing theories.

First, the reported positive effects of trust on cooperation is explained through the principle of reciprocity, that posits that individuals cooperate more facing cooperative partners [@Fehr2002; @VanLange1999]. Since in real-life situations it is not always possible to know exactly others' willingness to contribute, trust (i.e. beliefs about how much others cooperate) becomes essential to decide how to behave [@Vuolevi2012]. Moreover, trust among participants of a common-pool setting is at core of the framework of @Poteete2010, aimed at explaining why commons can be successful.

Secondly, the influence of SVO on cooperation is due to the difference between pro-social and pro-self in the importance accorded to the relative benefits. More specifically, pro-social value more others' outcome and equality in outcomes than pro-self [@VanLange1999]. Moreover, the difference in weights accorded to the personal and others' outcome seem to be the only dissimilarity between pro-social and pro-self, because they process the cooperative interaction in the same way [@Fiedler2013].

The reviewed results did not provide a clear conclusion about gender effect on cooperation. However, existing theories would predict that women cooperate more than men, because, according to gender stereotypes, women are more communal and caring, while men are more agentic and performance-oriented [@Eagly2012]. In fact, groups partly composed by women display more solidarity and collaboration than all-men groups [@Westermann2005]. However, every experimental paradigm can trigger the participants' gender identity differently [@Sell2009], and for this reason this effect is subjected to several moderators.

Concerning social status, the analyzed studies showed that usually members of low-status groups cooperated more and showed more solidarity with others low-status members than high-status. Although this effect has not been extensively studied, these results seem to be consistent with the existing literature on social status. First, there are structural differences between high- and low-status group's dynamic, that make high-status members more individualistic than low-status [@Lorenzi-Cioldi2002]. High-status individuals also display more system justification and more Social Dominance Orientation than low-status [@Caricati2012; @Vargas-Salfate2018]: they see the social system as fair and they have a preference for inequality between social groups. This is negatively correlated with concern about others and altruism [@Pratto1994].

The last individual factor was group identification, and the reviewed results showed that the more individuals identify with their group, the more they are likely to act for the group's good. In fact, according to the Social Identity Theory, people's identity is also composed by their group affiliations, and the stronger they identify with a social group, the more important this group becomes for their identity and the more their personal interests aligns with group's ones [@Tajfel1974]. Also, within a social group, individuals perceive themselves as more similar to other members, and therefore they are more susceptible to adopt collective goals and behaviours [@Turner1984; @Fritsche2018]. Moreover, strongly identified people are less likely to leave a group in case of failure or difficulties [@Ellemers1997]. Thus, a strong identification is essential for a group's success. In-group identification is also essential to engage in collective actions [@VanZomeren2008], and it is the main predictor of pro-environmental actions in the Social Identity Model of Pro-Environmental Action [SIMPEA, @Fritsche2018].

## Factors' interactions

Until now, the identified factors have been discussed separately. However, their impacts are interconnected, as already anticipated in some reviewed results about moderation effects. For instance, there are gender differences in trust and SVO: trust is a better predictor of cooperation in women than in men [@Irwin2015; @Dorrough2019], and women are more prevalent between pro-social and less between pro-self [@VanLange1999]. Moreover, SVO and trust are linked [@Ackermann2019], and the expectancy about others' cooperation can even be seen as a part of the construct of SVO [@Bogaert2008]. Therefore, pro-self individuals show less cooperation in part because they expect others not to cooperate.

@@

Secondly, communication impacts several other factors. For instance, it plays an essential role in shaping social norms [@Bicchieri2002] and it can improve cooperation by signalling a person's intentions and trustworthiness [@Janssen2015]. Moreover, the opportunity to exchange about the strategies that need to be implemented improve people's commitment within a group, that is a component of group identification [@Postmes2001]. At the same time, group identification also moderates other effects. First, as a consequence of the Social Identity Theory, high-identified individuals are more willing to comply to the group's norms and to pursue the group's goal [@Tajfel1974]. Therefore, they need less cooperation-enhancing measures such as incentives [@VanVugt2009] or non-anonymous conditions [@Barreto2000]. Moreover, social rewards work better with people who strongly identify with the group that can approve their behaviour [@Kopelman2002].

@@

## Theoretical implications

The analyzed papers showed that people often cooperate. This contradicts the Rational Choice Theory (RCT), who posits that individuals are too self interested to sacrifice their personal benefit to the greater good, unless if forced to do so. Our general results are therefore consistent with the existing literature, since RCT has already been refuted by experimental studies, who demonstrated that cooperation was higher than predicted in social dilemmas, and that it was impacted by variables that should not play a role according to this theory [@Ostrom1998].

Moreover, this review also corroborated the lack of quantitative studies about cooperation in real-life commons: of the 89 analyzed papers, just three had these characteristics, and they all were correlative. Therefore, they could not draw a causal link between the investigated factors and cooperative behaviours. This confirms a gap in the literature, that could be filled by futures experimental studies about cooperation in commons. Moreover, this review laid the foundations to implement such experiment in real-life commons, by providing a set of factors that could be tested.

## Practical implications

This review can be used as a guide for commons members to design campaigns or activities to improve cooperation. In fact, some of the identified factors can be manipulated in order to create better conditions for cooperation to arise. Moreover, since the different elements are linked, they can impact cooperation both directly and indirectly, via mediation or moderation effects. Based on the quantity of connections with other elements, the factors that seem to have a stronger effect are trust, communication, group identification and accountability of actions. Therefore, interventions based on this elements can be very powerful tools to improve cooperation in commons. On the other hand, some individual factor cannot be manipulated, but must be taken into account when designing an intervention. For instance, commons' composition in terms of gender and social status can have a large influence on the overall cooperation.

# Limitations and future perspectives

To conclude, this review summarized existing researches about cooperation in social dilemmas, and therefore provided a set of factors that can help better understanding cooperative behaviours in commons. It also highlighted a lack of quantitative studies about this topic in real-life commons. It is, however, not without limitations.

First, there is a lack of representation of the global population. In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from Global North. The current results apply therefore to Western societies and should not be generalized to Global South. In fact, there are cultural differences in individualism and collectivism: generally, North American and European cultures are more individualistic, while South American, African and Asian ones are more collective [@Triandis1989]. These differences affect the extent to which individuals define themselves as part of a group [@Trafimow1991] and, consequently, their behavior in cooperative situations [e.g. @Kuwabara2014]. It is therefore likely that cooperation relies on different mechanisms in Global South and North: comparative studies between this two regions should be conducted in order to reach a global understanding of cooperation.

Moreover, our aim was to use results of social dilemma researches to gain a better understanding of commons, therefore most of the included studies had a laboratory setting. In fact, this kind of setting is very useful to study social dilemmas because it provides a standard paradigm [@Balliet2011]. However, this does not allow to exactly reproduce the dynamics of a commons [@Henry2011; @Cole2010]: some elements such as cultural factors and specific ecological conditions affecting the decision-making process cannot be reproduced in lab experiments [@Janssen2015]. Therefore, this paper offers a good basis about elements influencing cooperation in commons, but future studies should confirm these results in real-life settings. Moreover, this review is not informative about the relative importance of each factor. To shed light on this topic, quantitative studies are needed.

>>>>

<!--# PROBLEM: all my research questions are about social dilemmas, and the idea was to use this litterature to better understand cooperation in commons, however I also included papers that studied commons (in the search, one of the key words was "commons" => solution (?): in the methods section say that I also included commons literature for X,Y reasons (more completeness? see the rapport between the amount of SD and commons studies?) -->

@@

The way cooperation was operationalized was deeply connected to the study's setting. In fact, experiments based in laboratory often observed participants' distribution of resources between themselves and a group account to quantify their cooperation. The most used method (*N*=33) was to endow participants with an amount of a resource (often real or fictive money), and see which part they invested in a public account, from which the whole group could benefit. Otherwise, researchers observed which amount of the resource participants took for themselves from a collective pool (*N*=7), or how much they gave to another participant (*N*=4).[^5] Another method often used in laboratory studies was to give participants the choice between cooperation and defection (*N*=18). Interestingly, in laboratory settings, words like "cooperation" or "defection" were rarely used during the instructions, to avoid responses dictated by social desirability.

@@

<!--# in the text: tables with the name of factor, the papers, the main effect and a list of moderatorsin Annexe: same table, but with more details for each moderator effect is it useful to put in both tables the analyzed papers for each factor?for the word count: useful to put all the authors just in the Annexe table, and in the text letting only N=11-->

@@

|                                                               | @Dorrough2019; @Peshkovskaya2017; @Balliet2011; @Spadaro2023; @Sell2009; @Gomez-Ruiz2020; @Colman2018; @Peshkovskaya2019; @Barrero-Amortegui2021; @Simpson2003; @Irwin2015               |                                                                                                 | -   Group composition                                            |

@@

|                                                               | @Aksoy2019; @Kingsley2016; @VanLange2013; @Chen2022; @Camera2020; @VanKlingeren2021                                                                                                      |                                                                                                 | -   Group composition                                            |

@@

|                                                               | @Arora2016; @Noonan2016; @Gomez-Ruiz2020; @VanVugt2009; @Zhang2019; @Chen2007; @Wit1992; @Dorrough2015; @Aksoy2019; @Puurtinen2009; @Nockur2020; @Kramer1984; @Jackson2011; @Jackson2012 |                                                                                                 | -   Intergroup competition                                       |

@@

|                                                               | @Balliet2009; @Emonds2011; @VanLange1998; @DeKwaadsteniet2008; @Lu2019                                                                                                                   |                                                                                                 | -   Uncertainty about the number of members                      |
|                                                               |                                                                                                                                                                                          | Pro-environmental values are positively correlated to cooperation                               | -   Deliberation                                                 |
|                                                               | *N*=9 (other factors)\                                                                                                                                                                   |                                                                                                 | -   Inter- vs independent self                                   |
|                                                               | @Sussman2016; @Fosgaard2019; @Kieslich2014; @Hilbig2018; @Kocher2017; @Schlosser2018; @Liu2009a; @Probst1999; @Chen2007                                                                  | Left-wingers are more cooperative than right-wingers                                            | -   Perceived social norms                                       |

@@

|                                                               |                                                                                                                                                                                          | Individuals scoring high in humility and honesty cooperate more than those scoring low          |                                                                  |

@@

|                                                               |                                                                                                                                                                                          | Individuals with high self-control, or with a high level of justice sensitivity, cooperate more |                                                                  |

@@

|                                                               | @Balliet2013; @Lubke2021; @VanLange2013; @Kocher2015; @Smith2013; @Chaudhuri2002; @Oyediran2018; @Sturm2019; @Franzen2019; @Rompf2017                                                    |                                                                                                 | -   Uncertainty about others' intentions                         |

@@

## Group factors

On the group level, we identified four factors from the reviewed papers: incentives, communication, social norms and anonymity. As for the individual factors, in the following sections we detail the main effects of each factor, and we provide an overview of possible moderators. A remsume of the main effects can be found in Table 3, while more details about the moderators in Appendix A.

+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+

@@

+=======================+==================================================================================================================================================================================================================================================================+================================================================================+===============================================================+

@@

|                       | @Balliet2011a; @VanDijk2015; @Pfattheicher2018; @Nockur2021; @Egas2008; @Milinski2012; @Kingsley2016; @Chen2022; @Xiao2016; @Rockenbach2019; @VanDijk2015; @VanVugt2009; @Schlosser2018; @Irwin2014; @Mulder2006; @Jacquet2011; @Nelissen2013; @Maier-Rigaud2010 |                                                                                | -   Type of interaction                                       |
|                       |                                                                                                                                                                                                                                                                  |                                                                                | -   Other participants' characteristics and group homogeneity |

@@

+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+

@@

|                       | @Balliet2010; @Bicchieri2002; @Janssen2014; @Koessler2021; @Adams2022; @Hopthrow2005; @Kumakawa2013; @Torsvik2011; @Feinberg2014; @Feinberg2012; @Giardini2021                                                                                                   |                                                                                | -   Type of communication                                     |

@@

|                       | @VonBorgstede2018; @Thogersen2008; @Rege2004; @Arora2012; @VanLange2013; @Bardsley2005a; @Weber2008; @Bicchieri2002                                                                                                                                              |                                                                                |                                                               |
+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+

@@

|                       | @Wang2017; @Rege2004; @VanVugt2010a; @Butz2021; @Romano2016; @VonBorgstede2018; @Jiang2021; @Mosler1993; @Przepiorka2020; @Koessler2021a                                                                                                                         |                                                                                |                                                               |
+-----------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------------------------------------------------+---------------------------------------------------------------+

@@

The aim of the present paper was to synthesize the existing literature about cooperation in social dilemmas, in order to identify factors that could impact cooperative behaviours in commons. More specifically, we aimed at identifying factors at the individual and group level that affect people's cooperation, as well as the moderating effects existing between them. Through a scoping review approach, we identified five individual, and four group factors.

<!--# in general I have some doubts about the order: what I did now is to follow the order of the research questions, namely: individual, group, moderationsHowever, I could not "include" the individual factors on the theories used in the introduction, while the group factors fit well in Ostrom principles. I find therefore strange to start from the factors that are less linked to the previous theories. At the same time it is normal that I did not find a lot of theories on individual factors for the introduction, because that's the gap that I foundSO: maybe it could be useful to change the order of the research questions and of the results? -->

<!--# discussion with Steffi: since in the introduction I did not use any theory to explain the specific individual and group factors that I found (I still didn't know what I was going to find), I used some new theories in the discussion to show that my results make sense -->

The factors on the individual level were: gender, social status, social identification, SVO and other values and personality traits, and trust. In the following paragraph we will discuss their effects on cooperation, and the implications for the study of commons.

First, the reviewed results about gender did not provide a clear conclusion about its effect on cooperation. A possible explanation is that every experimental paradigm can trigger differently the participants' gender identity [@Sell2009], and this impacts the way in which they decide to behave. Gender effect on cooperation is therefore very dependent on the context. For instance, factors such as other participants' gender, or the overall group composition determine whether men or women are more cooperative. For this reason, when studying commoners' cooperation, it is essential to take into account the effects that gender could have.

The second identified factors is social status, and, once again, we obtained contradictory findings about its effect on cooperation. However, our analysis revealed that members of low-status groups show solidarity with other low-status individuals, while this does not happen in high-status groups. This is consistent with the existing literature on social status. First, there are structural differences between high- and low-status group's dynamic, that make high-status members more individualistic than low-status [@Lorenzi-Cioldi2002]. Second, high-status individuals display more system justification (i.e. they perceive the social system as fair) and more Social Dominance Orientation (i.e. they have a preference for inequality between social groups) than low-status [@Caricati2012; @Vargas-Salfate2018]. This is negatively correlated with concern about others and altruism [@Pratto1994]. For this reason, social status must also be taken into account when investigating cooperation, since the solidarity dynamics described above influence individuals' behaviours.

Third, we found a strong positive effect of social identification: the more individuals identify with their group, the more they are likely to act for the group's good. <!--# question: when I recall results in the discussion, do I need to put again the citations? --> This is in line with the Social Identity Theory [@Tajfel1974], which posits that people's identity is also composed by their group affiliations. Therefore, the strongest the identification with a group, the more personal interests are aligned with group's ones. Also, within a social group, individuals perceive themselves as more similar to other members, and therefore they are more susceptible to adopt collective goals and behaviours [@Turner1984; @Fritsche2018]. Thus, for a group's success, its members' identification is essential: for instance, strongly identified individuals are less likely to leave a group in case of failure or difficulties [@Ellemers1997]. Given its importance, strengthen the commoners' social identification could significantly improve their cooperation for the commons' good. Moreover, priming a common social identity is quite simple [e.g. @Kramer1984; @Zhang2019]: therefore, this could allow to enhance cooperation in an easy and cheap way.

Fourth, Social Value Orientation also impacts cooperation. More specifically, individuals with a pro-social orientation cooperate more than those pro-self oriented. In fact, pro-social value more equality in outcomes, while for pro-self is the personal gain which is more important [@VanLange1999]. In addition to SVO, there are other values and personality traits which impact cooperation, such as political orientation, justice sensitivity, and self-control. Interestingly, although personality trait are usually stable, it is possible to modify values and attitudes, for example by making the participant elaborate about them [@Petty1995]. This technique could therefore be used to improve cooperation in commons.

The last individual factor, trust, has also a clear effect on cooperation: the more individuals trust other members, the more they cooperate. This effect is explained through the principle of reciprocity,<!--# Lilla: reciprocity is problematic because I never mention it in the results, and that I should add it as explanation. However, in the results part I mentioned only what came out of the papers, and explications are included only if mentioned in one of the papers--> that posits that individuals cooperate more facing cooperative partners [@Fehr2002; @VanLange1999]. Since in real-life situations it is not always possible to know exactly others' willingness to contribute, trust (i.e. beliefs about how much others cooperate) becomes essential to decide how to behave [@Vuolevi2012]. For this reason, improving reciprocal trust between members of a commons can be a powerful tool to enhance cooperation.

In conclusion, individuals factors have a great impact on cooperation, although, to the best of our knowledge, just a few papers investigated them in the commons literature [e.g. @Nightingale2011; @Singh2017]. This scoping review contributed to this trend, showing that we cannot assume that, in a same situation, everybody behaves in the same way. Therefore, an individual-centered approach can provide great insights into cooperation in commons.

## Group factors

<!--# I put the principle in the same order as they are presented in the introduction, but I wonder if it is not better to follow the order of presentation of the different factors as I did in the previous section? -->

We identified four factors at the group level: incentives, communication, social norms, and anonymity. This factors will be discussed within Ostrom's seven design principles for a successful management of a common-pool resource [-@Ostrom1990]. Moreover, we will address their implications for the study of commons.

Ostrom's first principle about the need of clearly defined boundaries is linked to anonymity, since to define who has and who hasn't access to the resource commoners have to know each-other. Moreover, communication is also important to reach an agreement on the exact boundaries of the shared resource. The second and third principles posit that rules must be adapted to the resource condition, and that commoners must be able to participate in modifying them. What Ostrom calls "rules" is very close to social norms, and, once again, communication is essential to shape and adapt them according to the condition of the resource. The fourth and fifth principles are about a monitoring and a graduate sanction system, and they underline the importance of incentives, that can be both social or material. In fact, a monitor that discovers an infraction gains prestige by being a good member of the commons, while the rule-breaker loses it. At the same time, the monitor can often keep a portion of the violator's harvest. Moreover, these two systems discourage free-riding because commoners know that their actions can be observed by others. Finally, the sixth principle about arenas for conflict resolution is linked to communication.[^7]

[^7]: Since Ostrom's seventh principle concerns external authorities and institutions, the current scoping review did not find any evidence in its support.

The main implication of these results is that a classical work of commons literature, as it is Ostrom's seminal book, is confirmed with findings coming from other disciplines and (mostly) from experimental studies. This shows that integrating this approach on the study of cooperation in commons is pertinent, and can give additional interesting insights on the topic.

## Moderation effects between factors

<!--# mention the main factors identified? in that case, reformulate to have the main ones as main subject of each paragraph -->

Until now, the identified factors have been discussed separately. However, their impacts are often interconnected. In this section, we will show how they are linked to each other.

For instance, there are gender differences in trust and SVO: trust is a better predictor of cooperation in women than in men [@Irwin2015; @Dorrough2019], and women are more prevalent between pro-social and less between pro-self [@VanLange1999]. Moreover, SVO and trust are linked [@Ackermann2019], and the expectancy about others' cooperation can even be seen as a part of the construct of SVO [@Bogaert2008]. Therefore, pro-self individuals show less cooperation in part because they expect others not to cooperate.

<!--# in the precent version I did not have a specific research question about how factors are connected to each-other, so this part fitted well: I took the results and completed them with related literatureHowever, now that I do have a research question about the moderation, it feels strange to add new results in this part. Should I take here only the moderation effects identified in the results section? Or maybe should I start from what I found to further develop on other moderators? -->

@@

Secondly, communication impacts several other factors. For instance, it plays an essential role in shaping social norms [@Bicchieri2002] and it can improve cooperation by signalling a person's intentions and trustworthiness [@Janssen2015]. Moreover, the opportunity to exchange about the strategies that need to be implemented improve people's commitment within a group, that is a component of group identification [@Postmes2001]. At the same time, group identification also moderates other effects. First, consistent with the Social Identity Theory, high-identified individuals are more willing to comply to the group's norms and to pursue the group's goal [@Tajfel1974]. Therefore, they need less cooperation-enhancing measures such as incentives [@VanVugt2009] or non-anonymous conditions [@Barreto2000]. Moreover, social rewards work better with people who strongly identify with the group that can approve their behaviour [@Kopelman2002].

@@

The fact that factors are connected to each other means that their effect on cooperation can be either direct or indirect, via the moderation of other factors. This has important practical implications: first, it shows that, when implementing a strategy aimed at improving cooperation in commons, not all the factors need to be explicitly addressed. For instance, encouraging participants to communicate also improves their mutual trust, helps them to shape social norms, and increases their identification in the group. Second, these connections allow us to identify four central factors, namely trust, communication, group identification and anonymity. These "core" elements can be used as starting point for future researches about cooperation in commons, as well as for behavioural interventions to improve cooperation. On the theoretical level, the fact that individual and group factors are linked shows that integrating an individual perspective to the commons literature is important, and it can contribute to gain a better understanding of why people do (not) cooperate in commons.

# Conclusions, limitations and future perspectives

Beyond the specific factors, this review showed that people often cooperate. This contradict Hardin's [-@Hardin1968] assumptions that rational individuals are too self-interested to cooperate in a situation where individual and group interests are at odds. Our results are therefore consistent with the existing literature, namely with theories such as the Greed Efficience Fairness Hypothesis [@Wilke1991], the Humanistic Rational Choice Theory [@DeCaro2021], or the theory of competitive altruism [@Roberts1998], which posit that cooperation is possible. Moreover, several experimental studies have already demonstrated that cooperation was higher than predicted in social dilemmas, and that it was impacted by variables that should not play a role from a rational point of view [@Ostrom1998].

Moreover, this review made an important contribution to the study of commons through social dilemma experiments. In fact, previous studies using the same approach focused either on a specific commons [e.g. @Hartl2022] or on a specific discipline [@Kopelman2002]. We extended these results by studying cooperation in general, and by not excluding any scientific field.

Third, we also identify a lack of quantitative studies about cooperation in real-life commons: of the 89 analyzed papers, just three had these characteristics, and they all were correlative. Therefore, they could not draw a causal link between the investigated factors and cooperative behaviours. This confirms a gap in the literature, that could be filled by futures experimental studies about cooperation in commons. Moreover, this review laid the foundations to implement such experiment in real-life commons, by providing a set of factors that could be tested.

Concerning the review's limitations, we could identify three. First, there is a lack of representation of the global population. In fact, two thirds of the analyzed papers were studies conducted in Europe or in North America, and the fourteen reviews included were also mostly based on studies from occidental countries. The current results apply therefore to Western societies and should not be generalized to other cultures. In fact, there are cultural differences in individualism and collectivism: generally, North American and European cultures are more individualistic, while South American, African and Asian ones are more collective [@Triandis1989]. These differences affect the extent to which individuals define themselves as part of a group [@Trafimow1991] and, consequently, their behavior in cooperative situations [e.g. @Kuwabara2014]. It is therefore likely that, in different cultures, cooperation relies on different mechanisms: comparative studies between this two regions should be conducted in order to reach a global understanding of cooperation.

Secondly, our aim was to use results of social dilemma researches to gain a better understanding of commons, therefore most of the included studies had a laboratory setting. In fact, this kind of setting is very useful to study social dilemmas because it provides a standard paradigm [@Balliet2011]. However, this does not allow to exactly reproduce the dynamics of a commons [@Henry2011; @Cole2010]: some elements such as cultural factors and specific conditions affecting the decision-making process cannot be reproduced in lab experiments [@Janssen2015]. Therefore, this paper offers a good basis about elements influencing cooperation in commons, but future studies should confirm these results in real-life settings. Moreover, this review is not informative about the relative importance of each factor. To shed light on this topic, quantitative studies are needed.
